%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Simon Duff} \\ \vspace{1pt}
    \small +44 7817 085 621 $|$ \href{mailto:simontd13@gmail.com}{\underline{simontd13@gmail.com}} $|$ 
    \href{https://www.linkedin.com/in/simontduff/}{\underline{linkedin.com/in/simontduff}} $|$
    \href{https://github.com/SiDu-D2}{\underline{github.com/SiDu-D2}}
\end{center}

%-----------Statement-----------
\begin{center}
An experienced and skilled worker highly motivated to pivot my career to formal education and employment in Software Engineering. I am continuing to teach myself the fundamentals of programming with aspirations to work in front-end or back-end development.
\end{center}
%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
  \resumeSubheading
  {Harvard University}{Online}
    {Introduction to Computer Science CS50}{Sep 2022 - present}
     \resumeSubheading
  {The Odin Project}{Online}
    {Foundations Course}{Aug 2022 - present}
    \resumeSubheading
  {FreeCodeCamp.org}{Online}
    {Responsive Web Design}{Ongoing}
    

  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Civil Engineer}{Jan. 2021 - Present}
      {Transport Planning \& Engineering}{Glasgow, UK}
      \resumeItemListStart
        \resumeItem{Leading the design and project management for several active travel schemes throughout Scotland.}
        \resumeItem{Providing solutions to clients in the form of technical drawings, reports and costings to take projects from feasibility stage to construction.}
        \resumeItem{Communication with stakeholders such as local communities, landowners, funders, clients and local authorities to develop designs that will benefit and be inclusive of all users.}
      \resumeItemListEnd
      
% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------

    \resumeSubheading
      {Civil Engineer}{Sep. 2016 - Jan. 2021}
      {Mott MacDonald Ltd}{Glasgow, UK}
      \resumeItemListStart
        \resumeItem{Used Buildings Information Management to produce 3D models for new building projects.}
                \resumeItem{Became adept at an array of  software such as Excel VBA, Civil 3D (3D modelling), MicroDrainage (drainage simulations). }
        \resumeItem{Seven month secondment to Northumberland County Council Roads Design Team. Project management and design of several projects that included new road signs, road markings and surfacing. }
        \resumeItem{Six month secondment to Scottish Water technical services team. }
                \resumeItem{Formal training provided as part of graduate programme such as public speaking and project management.}
    \resumeItemListEnd

    \resumeSubheading
      {Trainee Engineer}{Jun. 2015 -- Sep. 2016}
      {Amey plc}{Motherwell, UK}
      \resumeItemListStart
        \resumeItem{Progression of AutoCAD skills in part-time role during final year of university.}
        \resumeItem{Designed pipes and drains for 10km of new motorway, the M8, between Glasgow and Edinburgh.}
        \resumeItem{Learned a landscape architecture software (KeySCAPE) over several weeks to present clients with planting drawings for new motorway.}
        \resumeItem{Weekly presentations of work to colleagues to demonstrate understanding and progress.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Skills/Hobbies}
    \resumeItemListStart
            \resumeItem{Programming projects include using HTML and CSS to build a recipe site and using Replit, React and Vite to create an employee team allocation site.}
            \resumeItem{I play rugby at Paisley RFC where I'm also the club secretary since 2021.}
            \resumeItem{I love the outdoors, cycling, running, hill-walking and dog-training.}
          \resumeItemListEnd




%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: JavaScript, HTML, CSS, C} \\
     \textbf{Frameworks}{: React} \\
     \textbf{Developer Tools}{: Git, VS Code, Replit} \\
    }}
 \end{itemize}


%-------------------------------------------
\end{document}
